Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Updates to methodology section

The Measurement Template is found in Appendix~\ref{SecGradingTemplate}.  This
template is used to track measurements and quality scores for all of the
software packages in the domain. For each software package, we fill out one
column of the template. This process can take between 1 to 4 hours for each
package.  Project developers can be contacted for help regarding installation,
if necessary, but a cap of about 2 hours should be imposed on the entire
installation process, to keep the overall measurement time feasible.  To save
time, a
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{blank
measurement template spreadsheet} has been prepared.  An excerpt of the
spreadsheet is shown in Figure~\ref{measurement_template_image}.

\begin{figure}[h!]
	\begin{center}
	  \includegraphics[width=1.0\textwidth]{measurement_template}
	  \caption{Excerpt of the Top of the Measurement Template}
	  \label{measurement_template_image}
	\end{center}
  \end{figure}

@@

Following the summary section to measure 9 qualities: 
\begin{inparaenum}
	\item installability;
	\item correctness and verifiability;
	\item surface reliability;
	\item surface robustness;
	\item surface usability;
	\item maintainability;
	\item reusability;
	\item surface understandability; and,
	\item visibility/transparency. \end}inparaenum} Definitions of these
qualities are available in a working document on software quality.  Explain the
use of the word surface.

@@

As in \citet{SmithEtAl2016}, Virtual machines (VMs) are used to provide an
optimal testing environments for each MGMP software product. VMs were used
because it is easier to start with a fresh environment without hav- ing to worry
about existing libraries and conflicts. Moreover, when the tests are complete
the VM can be deleted, without any impact on the host operating system. The most
significant advantage of using VMs is to level the playing field. Every software
install starts from a clean slate, which removes ``works-on-my-computer``
errors. In the grading data the details for each VM are noted, including
hypervisor and operating system version.

>>>>

The Measurement Template is found in Appendix~\ref{SecGradingTemplate}.  This
template is used to track measurements and quality scores for all of the
software packages in the domain. For each software package, we fill-in the
template questions. This process can take between 1 to 4 hours for each package.
Project developers can be contacted for help regarding installation, if
necessary, but a cap of about 2 hours should be imposed on the entire
installation process, to keep the overall measurement time feasible.  To save
time, a
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{blank
measurement template spreadsheet} has been prepared, with the measures as rows.
An excerpt of the spreadsheet is shown in
Figure~\ref{measurement_template_image}.  A column should be added to this
template for each software package to be measured.

\begin{figure}[h!]
	\begin{center}
	  \includegraphics[width=1.0\textwidth]{measurement_template}
	  \caption{Excerpt of the Top Section of the Measurement Template (Summary Information)}
	  \label{measurement_template_image}
	\end{center}
  \end{figure}

@@

Following the summary section are sections to measure 9 qualities: 
\begin{inparaenum}
	\item installability;
	\item correctness and verifiability;
	\item surface reliability;
	\item surface robustness;
	\item surface usability;
	\item maintainability;
	\item reusability;
	\item surface understandability; and,
	\item visibility/transparency. 
\end{inparaenum} 
Definitions of these qualities are available in a
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/QDefOfQualities/QDefOfQualities.pdf}{working
document on software quality}.  Several of the qualities use the word
``surface''.  This is to highlight that, for these qualities in particular, the
best that we can do is a shallow measure of the quality.  For instance, we are
not currently doing any experiments to measure usability.  Instead, we are
looking for an indication that usability was considered by the developers.  We
do this by looking for cues in the documentation, like a getting started manual,
a user manual and documentation of expected user characteristics.

@@

As in \citet{SmithEtAl2016}, Virtual machines (VMs) are used to provide an
optimal testing environments for each package. VMs were used because it is
easier to start with a fresh environment without having to worry about existing
libraries and conflicts. Moreover, when the tests are complete the VM can be
deleted, without any impact on the host operating system. The most significant
advantage of using VMs is to level the playing field. Every software install
starts from a clean slate, which removes ``works-on-my-computer`` errors. When
filling in the measurement template spreadsheet, the the details for each VM
should be noted, including hypervisor and operating system version.
